MSHS COVID-19 Vaccine Schedule Tracking

### 2021-10-12 Amb_Sched_Tracking.Rmd
Update analysis reference file. Change format of daily amb schedule tracking dashboard to include all scheduled doses.

---
output: html_document
---

### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking

@@

```{r Create template of sites and dates}
dates_2wks <- seq.Date(from = today - 1,
                       to = today + 14,
                       by = 1)

@@

@@

@@

```{r Subset dose 3 schedule data}
# Create dose 3 schedule summary for ambulatory team
dose3_sch_next_2wks <- sched_data %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate %in% dates_2wks &
           Dose == 3) %>%
  group_by(ApptDate, Site, Status2) %>%
  summarize(Count = n())

dose3_sch_next_2wks <- left_join(
  site_dates_templ,
  dose3_sch_next_2wks, 
  by = c("Site" = "Site",
         "Date" = "ApptDate")
)

dose3_sch_next_2wks <- dose3_sch_next_2wks %>%
  mutate(Count = replace_na(Count, 0),
         Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
                          ifelse(is.na(Status2) & Date >= today, "Sch",
                                 Status2)),
         Date = format(Date, "%m/%d/%y"))

dose3_sch_next_2wks_cast <- pivot_wider(dose3_sch_next_2wks,
                                        names_from = c(Status2, Date),
                                        names_sep = "_",
                                        names_sort = FALSE,
                                        values_from = Count)

dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS")

dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
  mutate_all(~replace_na(., 0))

col_names_df <- colnames(dose3_sch_next_2wks_cast)
col_names_table <- str_replace(col_names_df, regex("^[a-z]*_", ignore_case = TRUE), "")
arr_cols <- max(which(str_detect(col_names_df, "Arr"))) - min(which(str_detect(col_names_df, "Arr"))) + 1
sch_cols <- max(which(str_detect(col_names_df, "Sch"))) - min(which(str_detect(col_names_df, "Sch"))) + 1

kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
        align = "c", digits = 0,
        # caption = paste("Dose 3 Schedule"),
      col.names = col_names_table) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(dose3_sch_next_2wks_cast)),
                border_right = "thin solid lightgray") %>%
    add_header_above(c(" " = 1,
                       "Arrived Visits" = arr_cols,
                       "Scheduled Visits" = sch_cols),
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3]),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(dose3_sch_next_2wks_cast),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE) %>%
    scroll_box(width = "800px")

@@

```{r Create kable for scheduled appointments over next 14 days}

asis_output(paste0("<h4>Based on Epic schedule data as of ",
                   format(file.info(sched_data_file)$ctime,
                          "%m/%d/%y %I:%M %p"),
                   "</h4>"))

asis_output("<br>")
asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>")
kable_dose3_sch

asis_output("<br>")
asis_output("<br>")
asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ",
                   made_dates_str,
                   "</h4>"))

@@

>>>>

---
title: MSHS COVID-19 Vaccine Schedule Tracking
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
---

<!-- ### MSHS COVID-19 Vaccine Dose 3 Schedule Tracking -->

@@

```{r Create template of sites and dates}
# Create dataframe of dates for next 2 weeks
dates_2wks <- seq.Date(from = today - 1,
                       to = today + 14,
                       by = 1)

@@

# Create dataframe of doses
all_doses <- seq(from = 1, to = 3, by = 1)

doses_templ <- data.frame(
  "Dose" = rep(all_doses,
               length(all_sites)))

doses_templ <- doses_templ %>%
  arrange(Dose)

@@

# Combine site and doses
site_doses_templ <- data.frame(
  "Site" = rep(all_sites, length(all_doses)),
  "Dose" = doses_templ,
  stringsAsFactors = FALSE)

site_date_dose_templ <- left_join(site_dates_templ,
                                  site_doses_templ,
                                  by = c("Site" = "Site"))

@@

```{r Summarize schedule data by day and dose}
sched_summary <- sched_data %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate %in% dates_2wks) %>%
  group_by(Dose, Site, Status2, ApptDate) %>%
  summarize(Count = n(), .groups = "keep")

sched_summary <- left_join(site_date_dose_templ,
                           sched_summary,
                           by = c("Site" = "Site",
                                  "Date" = "ApptDate",
                                  "Dose" = "Dose"))

sched_summary <- sched_summary %>%
  mutate(Count = replace_na(Count, 0),
         Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
                          ifelse(is.na(Status2) & Date >= today, "Sch",
                                 Status2))) %>%
  arrange(Site, Date, Dose, Status2) %>%
  mutate(
    # Date = format(Date, "%m/%d/%y"),
         Dose = paste0("Dose", Dose))

sched_summary_table <- pivot_wider(sched_summary,
                                   names_from = c(Status2, Dose, Date),
                                   names_sep = "_",
                                   names_sort = FALSE,
                                   values_from = Count) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  pivot_longer(cols = contains("_"),
               names_to = c("Status2", "Dose", "Date"),
               names_sep = "_",
               values_to = "Count") %>%
  # arrange(Site, Date, Status2) %>%
  pivot_wider(names_from = c(Site, Status2, Date),
              names_sep = "_",
              names_sort = FALSE,
              values_from = Count) %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "AllDoses") %>%
  pivot_longer(cols = contains("_"),
               names_to = c("Site", "Status2", "Date"),
               names_sep = "_",
               values_to = "Count") %>%
  mutate(Site = factor(Site, levels = c(all_sites, "MSHS"), ordered = TRUE),
         Dose = factor(Dose, levels = c("Dose1", "Dose2", "Dose3", "AllDoses")),
         Count = replace_na(Count, 0),
         Date = as.Date(Date, format = "%Y-%m-%d")) %>%
  arrange(Site, Date, Status2) %>%
  mutate(Date = format(Date, "%m/%d/%y")) %>%
  pivot_wider(names_from = c(Status2, Date),
              names_sep = "_",
              names_sort = FALSE,
              values_from = Count) %>%
  adorn_totals(where = "col",
               na.rm = TRUE,
               name = "Total")

```{r Create a kable for each dose}

sched_data_kable <- function(dose) {
  kable_dose <- dose

  kable_dose_title <- ifelse(dose == "AllDoses", "All Doses",
                             str_replace(kable_dose, "Dose", "Dose "))

  sched_kable_df <- sched_summary_table %>%
  filter(Dose == kable_dose) %>%
  mutate(Dose = NULL)

  sched_summary_cols <- colnames(sched_kable_df)
  sched_summary_table_names <- str_replace(sched_summary_cols,
                                           regex("^[a-z]*_",
                                                 ignore_case = TRUE),
                                           "")

  arr_cols <- max(which(str_detect(sched_summary_cols, "Arr"))) -
    min(which(str_detect(sched_summary_cols, "Arr"))) + 1

  sch_cols <- max(which(str_detect(sched_summary_cols, "Sch"))) -
    min(which(str_detect(sched_summary_cols, "Sch"))) + 1

  sched_kable <- kable(sched_kable_df,
                       format = "html",
                       escape = FALSE,
                       align = "c",
                       digits = 0,
                       caption = paste(kable_dose_title, "Schedule"),
                       col.names = sched_summary_table_names) %>%
    kable_styling(bootstrap_options = "hover",
                  position = "center",
                  font_size = 11,
                  full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(sched_kable_df) - 1,
                           ncol(sched_kable_df)),
                border_right = "thin solid lightgray") %>%
    add_header_above(c(" " = 1,
                       "Arrived Visits" = arr_cols,
                       "Scheduled Visits" = sch_cols,
                       " " = 1),
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3],
                                    ""),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(sched_kable_df),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE) %>%
    column_spec(column = ncol(sched_kable_df),
                bold = TRUE,
                italic = TRUE) %>%
    scroll_box(width = "800px")

  return(sched_kable)
}

```{r Subset dose 3 schedule data}
# # Create dose 3 schedule summary for ambulatory team
# dose3_sch_next_2wks <- sched_data %>%
#   filter(Status2 %in% c("Arr", "Sch") &
#            ApptDate %in% dates_2wks &
#            Dose == 3) %>%
#   group_by(ApptDate, Site, Status2) %>%
#   summarize(Count = n())
# 
# dose3_sch_next_2wks <- left_join(
#   site_dates_templ,
#   dose3_sch_next_2wks, 
#   by = c("Site" = "Site",
#          "Date" = "ApptDate")
# )
# 
# dose3_sch_next_2wks <- dose3_sch_next_2wks %>%
#   mutate(Count = replace_na(Count, 0),
#          Status2 = ifelse(is.na(Status2) & Date < today, "Arr",
#                           ifelse(is.na(Status2) & Date >= today, "Sch",
#                                  Status2)),
#          Date = format(Date, "%m/%d/%y"))
# 
# dose3_sch_next_2wks_cast <- pivot_wider(dose3_sch_next_2wks,
#                                         names_from = c(Status2, Date),
#                                         names_sep = "_",
#                                         names_sort = FALSE,
#                                         values_from = Count)
# 
# dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
#   adorn_totals(where = "row",
#                na.rm = TRUE,
#                name = "MSHS") %>%
#   adorn_totals(where = "col",
#                na.rm = TRUE,
#                name = "Total")
# 
# dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
#   mutate_all(~replace_na(., 0))
# 
# col_names_df <- colnames(dose3_sch_next_2wks_cast)
# col_names_table <- str_replace(col_names_df, regex("^[a-z]*_", ignore_case = TRUE), "")
# arr_cols <- max(which(str_detect(col_names_df, "Arr"))) - min(which(str_detect(col_names_df, "Arr"))) + 1
# sch_cols <- max(which(str_detect(col_names_df, "Sch"))) - min(which(str_detect(col_names_df, "Sch"))) + 1
# 
# kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
#         align = "c", digits = 0,
#         # caption = paste("Dose 3 Schedule"),
#       col.names = col_names_table) %>%
#   kable_styling(bootstrap_options = "hover",
#                 position = "center",
#                 font_size = 11,
#                 full_width = FALSE) %>%
#   column_spec(column = c(1,
#                          ncol(dose3_sch_next_2wks_cast) - 1,
#                          ncol(dose3_sch_next_2wks_cast)),
#               border_right = "thin solid lightgray") %>%
#   add_header_above(c(" " = 1,
#                      "Arrived Visits" = arr_cols,
#                      "Scheduled Visits" = sch_cols,
#                      " " = 1),
#                    background = c("",
#                                   sinai_colors[1],
#                                   sinai_colors[3],
#                                   ""),
#                    line = FALSE,
#                    color = "white") %>%
#   row_spec(row = nrow(dose3_sch_next_2wks_cast),
#            bold = TRUE,
#            italic = TRUE,
#            hline_after = TRUE) %>%
#   column_spec(column = ncol(dose3_sch_next_2wks_cast),
#            bold = TRUE,
#            italic = TRUE) %>%
#   scroll_box(width = "800px")

@@

## Vaccine Schedules by Dose

### All Doses
```{r Call custom function for schedule for all doses}
sched_data_kable(dose = "AllDoses")

<br>

### Dose 1
```{r Call custom function for schedule for dose 1 appointments}
sched_data_kable(dose = "Dose1")

<br>

### Dose 2
```{r Call custom function for schedule for dose 2 appointments}
sched_data_kable(dose = "Dose2")

<br>

### Dose 3
```{r Call custom function for schedule for dose 3 appointments}
sched_data_kable(dose = "Dose3")

```
<br>
<br>

## Appts Made Yesterday & Today

### Dose 3 Appts: All Statuses
```{r Create kable for scheduled appointments over next 14 days}

# asis_output(paste0("<h4>Based on Epic schedule data as of ",
#                    format(file.info(sched_data_file)$ctime,
#                           "%m/%d/%y %I:%M %p"),
#                    "</h4>"))
# 
# asis_output("<br>")
# asis_output("<h4>Dose 3 Schedule for Next Two Weeks</h4>")
# kable_dose3_sch
# 
# asis_output("<br>")
# asis_output("<br>")
# asis_output(paste0("<h4>Dose 3 Schedule for Appointments Made On ",
#                    made_dates_str,
#                    "</h4>"))

@@

### Dose 3 Appts: Arrived & Scheduled Only
```{r Test}
